Pillar 2 - (STM) Topic Modeling

### 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd

```
##Fit new docs
```{r}
model <- stm_model %>% filter(`Topic ID`=="overview_10")%>%
  pull(Model)

model <- model[[1]]

# fitting:
out <- asSTMCorpus(fasos_cast)

newdocs <- alignCorpus(new=out, old.vocab = model$vocab)

fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix

plot.STM(model, type ="summary")

fasos_theta$theta #nice kind of makes sense

>>>>

```
##Fit new docs
```{r}
model <- stm_model %>% filter(`Topic ID`=="overview_10")%>%
  pull(Model)
model <- model[[1]]

# fitting:
out <- asSTMCorpus(fasos_cast)
newdocs <- alignCorpus(new=out, old.vocab = model$vocab)
fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix

my_names <- names(newdocs$documents)

fasos_theta$theta #nice kind of makes sense
plot.STM(model, type ="summary")

rownames(fasos_theta$theta) <- my_names

new_courses_theta <- fasos_theta$theta
set_names(fasos_theta$theta, old = colnames(fasos_theta$theta), new = paste0("Topic", 1:10))
new_courses_theta %>%  mutate(Topic = paste("Topic_" rownames))
```
